### 2010-06-30 paper/IIWAS2010/content/related_work.tex
latest

Question Answering (QA) is an old field and there has been a recent influx of QA work. The earliest question answering systems include BASEBALL \cite{Green1961} and Lunar \cite{woods1973} were both \emph{closed domain} and \emph{closed corpus}.  Closed domain QA systems are those in which the possible meanings of the questions given are finite. We define closed corpus sytems as those in which the sources used to answer questions are finite.  QA systems that treat the web as a document collection are open corpus systems.  The morpheus system is considered an open corpus system.  It goes beyond current state of the art QA systems by examining deep web sources.

Several community QA systems have been developed, one of the most popular being Yahoo! Answers \cite{yahooanswers2008}.  These sites enlist a community of users to answer question posed by other users.  This idea has evolved to invent socially integrated QA systems such as Aardvark \cite{vark2010}. In addition to having questions answered by users, Aardvark is able to contact potential question answerers through several media beyond webpages (e.g. instant messages, mobile phones).  This allows for possibly faster answers to questions.  The morpheus system relies on both user interface and the property of similar question being answered by a community of users to give a fast reliable answer.

@@

An ontology formally models real world \textit{concepts} and their
relationships. A concept or class in an ontology gives us an abstract and
simplified view of the world\cite{Gruber1993} in a machine-readable and
language-independent format. The relationships and attributes of an
ontological concept are defined using \textit{properties} and \textit{property
restrictions}. An ontology definition contains all of
these: classes, properties, and restrictions. A class in an ontology can have
multiple \textit{super classes} and \textit{sub-classes}. Finally, a
\textit{knowledge base} represents an ontology together with 
instances of its classes.

The DBpedia\footnote{http://dbpedia.org} project is based on extracting 
semantic information from the Wikipedia and making it available on the Web. 
Wikipedia semantics includes info-box templates, categorization information, 
images, Geo-coordinates, links to external Web pages, disambiguation pages, 
and redirects between pages in Wiki markup form \cite{Bizer2009}. 
DBpedia represents the Wikipedia categories using skos:concepts and category 
relations using skos:broader \cite{Bizer2009}. In fact, 
DBpedia does not define any new relations between the Wikipedia categories. 
The Wikipedia categories are extracted directly from Wikipedia pages, and there 
is no quality check on the resultant ontology. Similarly, additional ontological 
relations in DBpedia are generated from the info-box attributes and their values.

YAGO is a semi-automatically constructed ontology from the Wikipedia pages, info-boxes, categories and WordNet\footnote{http://wordnet.princeton.edu} synsets heterarchy\cite{Suchanek2009phd}. YAGO uses the Wikipedia page titles as its ontology individuals and categories as its ontology classes. The ontology's heterarchy is built using the \textit{hypernym} and \textit{hyponym} relations of the WordNet synsets. YAGO uses only the nouns from WordNet and ignores the WordNet verbs and adjectives. The connection between a WordNet synset and a Wikipedia category is achieved by parsing the category names and matching the parsed category components with the WordNet synsets\cite{Suchanek2009phd}. Those Wikipedia categories having no WordNet match are ignored in the YAGO ontology.

However, YAGO type extraction assumes that each Wikipedia page has at least one tagged category, and the assigned Wikipedia categories are relevant to that Wikipedia page. The Wikipedia page category assignments are subjectively assigned by human editors and some Wiki pages are unassigned i.e., they have no category. In addition, we cannot fully rely on the relevance of these assigned Wikipedia page categories. In addition, YAGO concentrates mainly on the fields of people, cities, events, and movies\cite{Suchanek2009phd}.

>>>>

The earliest question answering systems such as BASEBALL \cite{Green1961} and Lunar \cite{woods1973} had \emph{closed domains} and \emph{closed corpora}, that is, they supported finitely many questions on copora containing a fixed set of documents.
Morpheus uses the web as its dynamic, open corpus and examines deep web sources 
to answer questions.

Several community QA systems have been developed, such as Yahoo! Answers \cite{yahooanswers2008}. These sites enlist a community of users to answer questions posed by other users.  This idea has led to socially integrated QA systems such as Aardvark \cite{vark2010}. In addition to having questions answered by users, Aardvark can contact potential question answerers through media beyond web pages (e.g. instant messages, mobile phones).  This allows for faster responses to questions.  Morpheus relies on both its user interface and previous similar questions answered by a community of users to give a fast reliable answer.

@@

% This section needs to be reworked. It should be about 1 paragraph. It should define
% what these (ontology, dbpedia, wordnet) mean to morpheus
% What rigors boone invest to my pyramids? <<-- randomly generated

%An ontology formally models real world \textit{concepts} and their relationships. A concept or class in an ontology gives us an abstract and simplified view of the world\cite{Gruber1993} in a machine-readable and language-independent format. The relationships and attributes of an ontological concept are defined using \textit{properties} and \textit{property restrictions}. An ontology definition contains all of these: classes, properties, and restrictions. A class in an ontology can have multiple \textit{super classes} and \textit{sub-classes}. Finally, a \textit{knowledge base} represents an ontology together with instances of its classes.

%% use dbpedia instead of wikipedia here

The DBpedia\footnote{http://dbpedia.org} project is based on a community of contributors extracting semantic information from the Wikipedia and making it available on the Web.  Wikipedia semantics includes info-box templates, categorization information,  images, Geo-coordinates, links to external Web pages, disambiguation pages, and redirects between pages in Wiki markup form \cite{Bizer2009}.  DBpedia does not define any new relations between the Wikipedia categories.

%Morpheus uses the DBpedia categories and its semantics to construct its ontology.
%  DBpedia represents the Wikipedia categories using skos:concepts and category relations using skos:broader \cite{Bizer2009}. In fact,  DBpedia does not define any new relations between the Wikipedia categories.  The Wikipedia categories are extracted directly from Wikipedia pages, and there  is no quality check on the resultant ontology. Similarly, additional ontological relations in DBpedia are generated from the info-box attributes and their values.

YAGO is a semi-automatically constructed ontology from the Wikipedia pages, info-boxes, categories and WordNet\footnote{http://wordnet.princeton.edu} synsets heterarchy \cite{Suchanek2009phd}. YAGO uses the Wikipedia page titles as its ontology individuals and categories as its ontology classes. YAGO uses only the nouns from WordNet and ignores the WordNet verbs and adjectives.  YAGO discovers connections between a WordNet synsets and a Wikipedia categories parsing the category names and matching the parsed category components with the WordNet synsets. Those Wikipedia categories having no WordNet match are ignored in the YAGO ontology.  The ontology's heterarchy is built using the \textit{hypernym} and \textit{hyponym} relations of the WordNet synsets.

We have attempted to use similar techniques to construct ontologies for question answering realms.  Thus far, these ontologies can be use to classifiy terms, but their classes do not appropriately categorize deep web query parameters. Therefore we have been relegated to manually generating ontologies.  % TODO - add "this is under investigation"

%Morpheus uses many of the same ideas made when using YAGO to develop its own ontology as explained in Section \ref{sec:ontology_corpora}.

%However, YAGO type extraction assumes that each Wikipedia page has at least one tagged category, and the assigned Wikipedia categories are relevant to that Wikipedia page. The Wikipedia page category assignments are subjectively assigned by human editors and some Wiki pages are unassigned i.e., they have no category. In addition, we cannot fully rely on the relevance of these assigned Wikipedia page categories. In addition, YAGO concentrates mainly on the fields of people, cities, events, and movies\cite{Suchanek2009phd}.

### 2010-06-30 paper/IIWAS2010/content/results_discussion.tex
latest

\subsection{Discussion}

>>>>

First, we created an ontology for the automotive realm exploiting the Wikipedia pages, categories, and WordNet synsets. For each of the classes in the ontolgy we built corpora from the corresponding Wikipedia pages. Table describes the question answering process for the user query, ``A 1997 Toyota Camry V6 needs what size tires?''

%% TODO - need to refer back to the table which is figure one.
The Morpheus NLP engine parses this query into the constructs: WH:what,
Descriptive Information:1997 Toyota Camry V6, Asking For:size tires. From the
descriptive info, we generate the N-grams or terms 1997, 1997 Toyota, 1997
Toyota Camry,Toyota,Toyota Camry,Toyota Camry V6, Camry, Camry V6, and V6. For
each of the terms, we determined relevant categories (non-increasing order of
relevance) from the ontology corpora. Table \ref{tbl:term_categories} shows
the top categories and their probabilities for each of the query term:

\begin{table}[h]\footnotesize

\begin{tabular}{| p{3.2cm} | l | r |}
\hline 
Term & Category & $P(Category|Term)$ \\ \hline
1997 & Sedans & 404132.77e-14\\ 
1997 Toyota & Engines & 7.90e-14\\ 
Toyota  & Sedans & 3486670.15e-14\\ 
Toyota Camry & Sedans & 12147.23e-14\\ 
Toyota Camry V6 & Coupes & 13.80e-14\\ 
Camry & Sedans & 312034.20e-14\\ 
Camry V6 & Coupes & 13.80e-14\\ 
V6 & Sedans & 4464535.40e-14\\ \hline
\end{tabular}

\caption{Terms' top categories and probabilities}
\label{tbl:term_categories}

\end{table}

We found the top category of the terms in the candidate SSQ and determined the category divergence with the qualified SSQ classes in the QRM store. Then, we combined the divergence measure and
ranked QRMs based on the relevance score. Table \ref{tbl:ranked_queries} shows the top ranked SSQ for the query.  Finally, we execute the selected QRM and display the results to the user.

\begin{table}[h]\footnotesize

\begin{tabular}{| p{3.5cm} | p{3cm} | r |}
\hline
Query & Tagged Classes & Score\\ \hline
A 1997 Toyota Camry V6 needs what size tires? & IC:Sedans, Cars, Engines, Manufactures OC:size tires & 0.91\\ \hline 
What is the tire size for a 1998 Sienna XLE Van? & IC:Vans, Manufactures OC: tire size & 0.72\\ \hline 
Where can I buy a headlight for a Toyota Camry V6? & IC:Manufactures, Sedans, Engines OC: where & - \\ \hline 
What is the cost of a Toyota Camry V6 muffler? &  IC:Manufactures, Sedans, Engines OC: the clost  & - \\ \hline
\end{tabular}

\caption{Top ranked queries and relevance scores: IC - input classes, OC - output classes}
\label{tbl:ranked_queries}

\end{table}

%\subsection{Discussion}
\section{Conclusion}

In this paper, we propose a novel question answering system that uses the deep web and previously answered user queries to answer similar questions. The system uses a path finder to annotate answer paths so path followers can discover answers to similar questions.  Each $(question, answer)$ pair is assigned a realm, and new questions are matched to the new $(question, answer)$ pairs. Classification of terms into classes is based on term frequency distributions in our corpora of web documents. We are investigating improvements to our solution by an approach similar to Topic Models \cite{Blei2003latentdirichlet}.

Manually forming a corpus of wilipedia pages associated with a class is a cumbersome task. Topic Modeling provides a promising approach to identifying pages relevent to given class in a more automated manner.
%The Wikipedia page categories has limitations. Without supervision, the page categorization is often a challenging problem, because topics in the pages that belong to a realm (e.g. automotive) usually overlap. So we are evaluating the applicability of probabilistic topic models to web page categorization, and automatic generation of a realm-ontology based on the topics being extracted.
